Realistically Interesting Domains for Probabilistic Planners

### 2014-04-08 FinalPaper/paper.tex
rewrote introduction and changed order of section domains and section planners

\section{Introduction}

Since the first the International Probabilistic Planning Competition (IPPC),
problems have undergone radical changes. Dominating planners of previous
incorporations had a strong focus on goal-oriented MDPs, determinizing and
using powerful classical planners (e.g. FF \cite{Hoffmann01theff}) and
replanning. New benchmark problems have demonstrated weaknesses in existing
solution techniques.

Little and Thi\'ebaux have developed a baseline test in
\cite{little2007probvsreplan} to evaluate the problems of the fifth International
Planning Competition (IPC-5). This test determines if a planning problem is
`probabilistically interesting'. Problems that fail this test are classical
planning problems in disguise. Knowing this it is easy to design a problem
where a replanner performs badly or incredibly well.

The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
which can design domains that are more probabilistically interesting. The top
performers were PROST \cite{keller2012prost} and \textsc{Glutton}
\cite{kolobov2012glutton}.

While it is interesting to make problems harder and invent better planning
algorithms to solve those probabilistic complex problems, we evaluate whether
or not these problems are coherent with real-world situations.

The main contribution of this paper is an evaluation of FF-Replan versus a
probabilistically state of the art planner \textsc{Gourmand} in the realistically
augmented domains of IPPC-11. If these domains fail the baseline test proposed
by Little et al\., they would translate to classical planning problems in
disguise and could be easily solved by FF-Replan.

@@

\section{Problem formulation}

@@

\section{Domain Description}

@@

\myworries{misschien moet dat laatste zinnetje ergens anders?}

\section{Domains}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et al.'s baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.

>>>>

\section{Introduction}
The introduction of the International Planning Competition (IPC) in 1998 furthered the field of automated planning and scheduling. Since then several state-of-the-art planners such as the FF-planner \cite{Hoffmann01theff} have been introduced optimized for the initial classical planning problems. Surprisingly well-performing planners have caused the field to readjust the then supposedly challenging domains to provide a challenge for a wide variety of planners. By doing so, the definition of an interesting planning problem has been modified.

The entrance of FF-Replan \cite{FFReplan}, a replanner based on determinization techniques and the classical FF planner, surprisingly outperformed other participating MDP solvers in the International Probabilistic Planning Competition (IPPC) '04. As a result, Little et al. have argued for \emph{probabilistically interesting} domains \cite{little2007probvsreplan} and finite horizon MDPs were employed in IPPC-11. These approximations of infinite planning problems however strongly resemble optimization problems rather than the goal oriented initial planning domains.  This shift in the current interesting domains caused the state-of-the-art planners to cope with the large branching factors that are introduced using finite horizon MDPs.

This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem. An interesting currently relevant domain is proposed and evaluated amongst previously defined domains. By using the probabilistic interestingness baseline test as introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.

Section \ref{sec:problem} introduced the problem formulation this paper addresses while Section \ref{sec:domaind} introduces the details of proposed domain. Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:domains} and \ref{sec:planners} the interesting domains and planners respectively. Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up. Finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.

%Little and Thi\'ebaux have developed a baseline test in
%\cite{little2007probvsreplan} to evaluate the problems of the fifth International
%Planning Competition (IPC-5). This test determines if a planning problem is
%`probabilistically interesting'. Problems that fail this test are classical
%planning problems in disguise. Knowing this it is easy to design a problem
%where a replanner performs badly or incredibly well.
%While it is interesting to make problems harder and invent better planning
%algorithms to solve those probabilistic complex problems, we evaluate whether
%or not these problems are coherent with real-world situations.
%The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
%which can design domains that are more probabilistically interesting. The top
%performers were PROST \cite{keller2012prost} and \textsc{Glutton}
%\cite{kolobov2012glutton}.

%The main contribution of this paper is an evaluation of FF-Replan versus a
%probabilistically state of the art planner \textsc{Gourmand} in the realistically
%augmented domains of IPPC-11. If these domains fail the baseline test proposed
%by Little et al\., they would translate to classical planning problems in
%disguise and could be easily solved by FF-Replan.

@@

\section{Problem formulation}
\label{sec:problem}

@@

\section{Domain Description}
\label{sec:domaind}

@@

\section{Domains}
\label{sec:domains}

Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et al.'s baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
